PeakNet: An Autonomous Bragg Peak Finder with Deep Neural Networks

### 2023-06-30 manuscript.natcomm.tex
Handling repeated referencing.

When processing Rayonix images with $1920 \times 1920$ pixels, \peaknet{} achieved a significantly reduced processing time of 90 milliseconds per event on an NVIDIA 1080 Ti GPU.  In contrast, \psocake{} required 176 milliseconds per event when executed on an Intel E5-2620 CPU.  Another peak finding method, RPF (robust peak finder), operating on Intel E5-2698, is reported to require 120 milliseconds but on a smaller AGIPD 1M images \citep{hadian-jaziDataReductionSerial2021}.  This result clearly demonstrates that \peaknet{} not only delivers robust Bragg peak finding results in an autonomous fashion, but also exhibits remarkable runtime efficiency.  %This establishes it as a highly competent tool for real-time autonomous Bragg peak finding.

\begin{table*}[t]
\caption{
    The runtime performance of diffraction image analysis algorithms measured on
    Rayonix images containing 3.7 megapixels.  We measured runtime performance
    of \psocake{} and \peaknet{} directly using Rayonix images.  For reference
    purposes, we also included another peak finding method RPF
    \citep{hadian-jaziPeakfindingAlgorithmBased2017,
    hadian-jaziDataReductionSerial2021} and two classification methods for X-ray
    diffraction data reduction. RPF runtime performance was originally measured
    on AGIPD 1M \citep{allahgholiAdaptiveGainIntegrating2019}.  
}
\label{tb : runtime}
\centering
\resizebox{!}{!}{
\begin{tabular}{llcc}
\hline
Methods             & Hardware       & Image size         & Time (ms/event) \\ \hline
\peaknet{}          & NVIDIA 1080 Ti & 1920 $\times$ 1920 & 90.0            \\ \hline
\psocake{}          & Intel E5-2620  & 1920 $\times$ 1920 & 175.5           \\ \hline
RPF                 & Intel E5-2698  & 1024 $\times$ 1024 & 120.0           \\ \hline
%CNN hit finder      & Hit Finding  & NVIDIA 1080 Ti & 720 $\times$ 720   & 0.8             \\ \hline
%ORB+MLP             & Hit Finding  & Intel Core i5  & 720 $\times$ 720   & 50.0            \\ \hline
\end{tabular}
}
\end{table*}

>>>>

When processing Rayonix images with $1920 \times 1920$ pixels, \peaknet{} achieved a significantly reduced processing time of 90 milliseconds per event on an NVIDIA 1080 Ti GPU for peak finding and auto-mask generation.  In contrast, \psocake{} required 176 milliseconds per event when executed on an Intel E5-2620 CPU.  To provide a reference, an earlier study \citep{hadian-jaziDataReductionSerial2021} also reported the runtime efficiency of both the Robust Peak Finder (RBF) and Cheetah, demonstrating an average processing time of around 120 milliseconds for 3 times smaller AGIPD 1M \citep{allahgholiAdaptiveGainIntegrating2019} images.  It should be noted that computation time would be even longer if the auto-masking feature is introduced to these existing peak finders. This result clearly demonstrates that \peaknet{} not only delivers robust Bragg peak finding results autonomously but also exhibits remarkable runtime efficiency.

\begin{table*}[t]
\caption{
    The runtime performance of diffraction image analysis algorithms measured on Rayonix images containing 3.7 megapixels.  We measured runtime performance of \psocake{} and \peaknet{} directly using Rayonix images.  For reference purposes, we also included peak finding methods RPF and Cheetah, whose runtime performance were originally measured on AGIPD 1M.
}
\label{tb : runtime}
\centering
\resizebox{!}{!}{
\begin{tabular}{lllcc}
\hline
Methods         &  Auto-mask   & Hardware       & Image dimension    & Time (ms/event) \\ \hline
\peaknet{}      &  Yes         & NVIDIA 1080 Ti & 1920 $\times$ 1920 & 90.0            \\ \hline
\psocake{}      &  No          & Intel E5-2620  & 1920 $\times$ 1920 & 175.5           \\ \hline
RPF             &  No          & Intel E5-2698  & 1024 $\times$ 1024 & 120.0           \\ \hline
Cheetah         &  No          & Intel E5-2698  & 1024 $\times$ 1024 & 120.0           \\ \hline
%CNN hit finder      & Hit Finding  & NVIDIA 1080 Ti & 720 $\times$ 720   & 0.8             \\ \hline
%ORB+MLP             & Hit Finding  & Intel Core i5  & 720 $\times$ 720   & 50.0            \\ \hline
\end{tabular}
}
\end{table*}

### 2023-06-30 manuscript.tex
Handling repeated referencing.

When processing Rayonix images with $1920 \times 1920$ pixels, \peaknet{} achieved a significantly reduced processing time of 90 milliseconds per event on an NVIDIA 1080 Ti GPU for peak finding and auto-mask generation.  In contrast, \psocake{} required 176 milliseconds per event when executed on an Intel E5-2620 CPU.  To provide a reference, an earlier study \citep{hadian-jaziDataReductionSerial2021} also reported the runtime efficiency of both the Robust Peak Finder (RBF) and Cheetah, demonstrating an average processing time of around 120 milliseconds for 3 times smaller AGPID 1M images.  It should be noted that computation time would be even longer if the auto-masking feature is introduced to these existing peak finders. This result clearly demonstrates that \peaknet{} not only delivers robust Bragg peak finding results autonomously but also exhibits remarkable runtime efficiency.

\begin{table*}[t]
\caption{
    The runtime performance of diffraction image analysis algorithms measured on Rayonix images containing 3.7 megapixels.  We measured runtime performance of \psocake{} and \peaknet{} directly using Rayonix images.  For reference purposes, we also included peak finding methods RPF and Cheetah, whose runtime performance were originally measured on AGIPD 1M \citep{allahgholiAdaptiveGainIntegrating2019}.
}
\label{tb : runtime}
\centering
\resizebox{!}{!}{
\begin{tabular}{lllcc}
\hline
Methods         &  Auto-mask   & Hardware       & Image dimension    & Time (ms/event) \\ \hline
\peaknet{}      &  Yes         & NVIDIA 1080 Ti & 1920 $\times$ 1920 & 90.0            \\ \hline
\psocake{}      &  No          & Intel E5-2620  & 1920 $\times$ 1920 & 175.5           \\ \hline
RPF             &  No          & Intel E5-2698  & 1024 $\times$ 1024 & 120.0           \\ \hline
Cheetah         &  No          & Intel E5-2698  & 1024 $\times$ 1024 & 120.0           \\ \hline
%CNN hit finder      & Hit Finding  & NVIDIA 1080 Ti & 720 $\times$ 720   & 0.8             \\ \hline
%ORB+MLP             & Hit Finding  & Intel Core i5  & 720 $\times$ 720   & 50.0            \\ \hline
\end{tabular}
}
\end{table*}

>>>>

When processing Rayonix images with $1920 \times 1920$ pixels, \peaknet{} achieved a significantly reduced processing time of 90 milliseconds per event on an NVIDIA 1080 Ti GPU for peak finding and auto-mask generation.  In contrast, \psocake{} required 176 milliseconds per event when executed on an Intel E5-2620 CPU.  To provide a reference, an earlier study \citep{hadian-jaziDataReductionSerial2021} also reported the runtime efficiency of both the Robust Peak Finder (RBF) and Cheetah, demonstrating an average processing time of around 120 milliseconds for 3 times smaller AGIPD 1M \citep{allahgholiAdaptiveGainIntegrating2019} images.  It should be noted that computation time would be even longer if the auto-masking feature is introduced to these existing peak finders. This result clearly demonstrates that \peaknet{} not only delivers robust Bragg peak finding results autonomously but also exhibits remarkable runtime efficiency.

\begin{table*}[t]
\caption{
    The runtime performance of diffraction image analysis algorithms measured on Rayonix images containing 3.7 megapixels.  We measured runtime performance of \psocake{} and \peaknet{} directly using Rayonix images.  For reference purposes, we also included peak finding methods RPF and Cheetah, whose runtime performance were originally measured on AGIPD 1M.
}
\label{tb : runtime}
\centering
\resizebox{!}{!}{
\begin{tabular}{lllcc}
\hline
Methods         &  Auto-mask   & Hardware       & Image dimension    & Time (ms/event) \\ \hline
\peaknet{}      &  Yes         & NVIDIA 1080 Ti & 1920 $\times$ 1920 & 90.0            \\ \hline
\psocake{}      &  No          & Intel E5-2620  & 1920 $\times$ 1920 & 175.5           \\ \hline
RPF             &  No          & Intel E5-2698  & 1024 $\times$ 1024 & 120.0           \\ \hline
Cheetah         &  No          & Intel E5-2698  & 1024 $\times$ 1024 & 120.0           \\ \hline
%CNN hit finder      & Hit Finding  & NVIDIA 1080 Ti & 720 $\times$ 720   & 0.8             \\ \hline
%ORB+MLP             & Hit Finding  & Intel Core i5  & 720 $\times$ 720   & 50.0            \\ \hline
\end{tabular}
}
\end{table*}
